\subsection*{State of the art}
The current state of educational robotics does seem promising, it does however also include a major obstacle before reaching the mass populous of school children.
In most of the studies seen the robot only works as a feedback provider to the children, and this task could in many circumstances be achieved by the use of 
a simulator, flash game or app. Which in all cases would be cheaper and easier to acquire for the schools given the robotics landscape seen today.
A pedagogical counter to this situation comes from Piaget and Papert in the form of constructionism and constructivism, the latter being the dominant at this point. 
Researchers are in addition to this driven by the belief that robots awaken a tremendous source of energy and motivation in children. 
Another benefit is the connection between abstract concepts and physical representation given by robots, this could be especially beneficial within STEM topics as 
they are usually very abstract and robots may therefore help by giving a concrete understanding of these concepts. 
Thus truly justifying robotics as a superior alternative to simulator etc. 

\bigskip\noindent
In the literature search there are some areas of lacking research. Namely research on students aged 11-12 and lack of empirical research involving the use of low cost robots in education. In general there is also a lack of research with good experimental design with a larger sample. In general the lack of research can partly be blamed on the cost of robots. The cheapest robot seems to be Lego Mindstorm. This robot construction kit costs 650 USD. 

\bigskip\noindent
In educational robotics we differentiate between academic performance and other skills. Academic performance concerns how school curriculum can be tough by using robots, while other skills are skills outside the curriculum. These are skills that you learn because of working with the robots. Often academic performance is the main goal when introducing robots to students while other skills are merely a bonus that is not even taken into account most of the time. 

\subsubsection*{Academic performance}

Topics that are taught with robotics as teaching aid are mostly within the STEM (science, technology, engineering and mathematics) category. Specifically Newton's Laws of Motion, distances, angles, kinematics, graph construction and interpretation, fractions, ratios and geospatial concepts is mentioned often. In the systematic review carried out in \cite{Benitti2012978} 80\% of the papers focus on these topics. The two remaining papers discuss basic evolution and teaching basic social skills to kids with autism and asperger syndrome. 

\bigskip\noindent
Most of the research done provides promising results. None have discovered that it worsens learning, but there are examples of it not making any difference compared to traditional methods. It is hard to pinpoint the factors that generates positive results. Researchers and schools are reluctant too implement robotics as a learning tool because of this lack of empirical evidence of it being helpful. As mentioned earlier robots are expensive and the school could rather use this money on more effective learning aids. Many think that this interest in robots is just a passing fad. 

\subsubsection*{Other skills}
These skills are not measured, as the research focus is on the curriculum, but these skills may have important benefits later in school and life.

\bigskip\noindent
Technical skills that are often taught when working with robotics are problem solving, logic and scientific inquiry. 

\bigskip\noindent
Mind tools are thinking skills, problem-solving skills and teamwork skills. \cite{Benitti2012978} Suggests these as main topics for future research. Many mention that skills such as these were improved when introducing robotics in education but more research is also needed to figure out how to train the specific skills separately. 
