\section{Execution of project}
This entire project was conducted from February to July 2014. During this time period we've created a pilot-project looking into the use of robotics in an educational setting with a focus on angles and how these can be taught.
All we have done leads up to a pilot test at the Trondheim International School (THIS), where we tested our hypothesis and how well suited the \chirp robot was in an educational setting. 
The contact established between the \chirp team and the school will hopefully help foster further research within educational robotics from the \chirp team.
%This chapter will provide a walkthrough of the different phases of this project. 
%
%This chapter will highlight some of the tasks needed to conduct this project. 
%Everything we have done has been done since february. This made our process long and intense. We have conducted a pre-project to find a relevant angle on robotics in education and then we have focused further into the specific field of robotics in maths education.

\paragraph{Literature Reviews}~\\	
In order to understand educational robotics state of the art we performed a literature study into educational robotics with a focus on mathematics. The setup for this review can be read in section~\ref{ch:literatureProcess}.
The applicability of robotics in a mathematics setting has proven itself over and over again. The results from the literature study lead us to focus more specifically on angles instead of mathematics in general.
We have chosen to focus on angles as it is one of the core concepts within mathematics, students tend to struggle with it, and visualization of angles can be achieved with the help of a robot.
After the state of the art literature review we identified the need for an additional literature study. This study was conducted in order to learn more about the current pedagogical theories and test setups, which would help us find a suitable approach to create a solid platform for this project and potential successors. 
%How we approached is described below. 
%We also want to get an idea of what way we can introduce robotics to a school.
%\input{introduction/process}
%Another lack in research is an explanation of how they taught the students. They may mention that they implemented a 1 year curriculum but don't provide any examples of tasks they created. It is therefore very hard to build upon and do further work on it. 


%\paragraph{Deciding on a specific topic}\label{sec:decideTopic}~\\

%A lot of topics can be learned using robotics. We have focused on mathematics. It is said that all math can be taught in some way with robotics. We present examples for some of them.

%\bigskip\noindent
 %with a robot can be achieved without to much trouble. 
%We have chosen to focus on angles as it is very basic, people struggle with it and using logo uses angles to decide how much to turn. It is therefore a natural starting point for our investigation in mathematics with robotics. 
%
%\bigskip\noindent
%As a pedagogical foundation we looked to research conducted by Seymour Papert, who is known for his early contributions to the field of educational robotics~\cite{papert1980mindstorms,papertGrant}.
%We also draw pedagogical reasoning behind angles and geometry from papert. The reason angles and geometry in general is easier is that a point rather than being defined as a place in space with no heading the robot that serves as the point here has a heading just like us humans. It can therefore be related to. 

%\section{Literature Study on available programming languages and pedagogy}
%\paragraph{Secondary Literature Study}~\\
%After deciding to investige the concept of angles we identified the need for a secondary literature study. 
%This study was conducted in order to learn more about the current pedagogical theories and test setups, which would help us find a suitable approach to create a solid platform for this project and potensial successors.

%Avsnittet virker som om det handler mer om det første literature studiet.
%In order to focus on the right points, learn about the pedagogic theory and testing setup, use a suitable approach and create a solid platform to work on we needed to conduct a literature review to find state of the art on educational robotics as well as pedagogic theory. 

\paragraph{Design and Development}~\\
In order to conduct this project we needed to develop several accessories for the \chirp and a tablet application for testing in an elementary school. 
Since this was considered a pilot-project for the \chirp robot we aimed at designing and developing a prototype with emphasis on expandability, modifiability and portability. 
%Vet ikke helt hvordan denne skal uttrykkes, eller den i det hele tatt bør bli med?
%We will find workarounds for the chirp that does not require major modifications to the chassis or default circuit board with sensors. 
We also needed to develop a small circuit to enable bluetooth communication between the robot and tablet application. 
All in all there was a lot of work to be done before a prototype would be ready for the experiment. 
%Tror ikke vi trenger å skrive så mye begrunnelser her, siden det meste kommer til å bli nevnt i design and development kapitlet. 
%as we found that compiling and uploading code to the ChIRP is not suitable for every school grade and we don't know which grade we will be working with, another point is that this application again should be easily expandable and implementable for different grade students.  

%Igjen, tror ikke vi trenger begrunnelse her. 
%\bigskip\noindent
%The design and development of this software and hardware will be a very demanding phase. Designing a new application from scratch can be very time-consuming([39] - Another master %.Mention hardware too REFERANSE). However we build upon LOGO so we have some guidance to what the functionality should entail. 

%Again we will not have time to create an optimal solution as this would require testing and then redesign etc. We aim to create an easily manageable and changeable platform to build upon in future research. 

\paragraph{Experiment}~\\
To answer our research questions we had to test the robot in a school context. We contacted several schools, had meetings with Ungt Entreprenørskap and other researchers at IDI responsible for attracting students to study at IDI, all of whom were interested in the project. The time frame of the project did however not fit within their existing schedules. Our supervisor (Pauline) had previously been in contact with Trondheim International School (THIS), and they were very enthusiastic about the project, very helpful throughout the whole project, and we were lucky to be able to conduct our experiment with their students. 
We had 2 meetings with the teacher of the class we were assigned before the experiment itself. In these meetings we discussed our tests and curriculum and got feedback which we used to improve our experiment. It was important for us to include teachers as the end goal is to integrate the robotic activities to normal schools.
The experiments were run at the end of the school year because of the long process of finding a school and developing the system. This resulted in a smaller experimental time span than initially intended.

