\chapter{Introduction}
Schools have problems with keeping students engaged and motivated courses related to science, and especially in mathematics. 
Norwegian students also perform poorly compared the students in the neighbouring countries in these courses~\cite{OECDPISA}.
%They also perform poorly to a large extent. 
Since the robotics business is growing all the time and educational robotics has been shown to have great promise we focus this project on an investigation into the potential of robotics in schools and make an effort to expand the \chirp team's horizon into the world of education. This thesis serves as an introduction into the educational world for the \chirp team at IDI. A lot of groundwork therefore had to be done in order to carry out this experiment, and we've focused on making the project applicable for future work.

\bigskip\noindent
A lot of research has been done to show that robotics can be beneficial in an educational setting.
Many researchers rely on the early work conducted by Seymour Papert within educational robotics, but often fail to fail to explain how Papert's theories are applied within their own research. 
%Many mention Papert, but fail to explain how their approach relates to his theories of learning.
%They merely state that Papert was an influence or that they use experimental design inspired by Papert's work. %, but this is only a small part of Papert's vision. 
Another common sight while reading about educational robotics is lack of research regarding the usefulness of a physical robots in itself, as it seems like most people made the jump from tradional teaching to teaching with a robot in one big jump. 
While still basing our approach on Papert's theories of mental model building, we will try to fill some of these holes. We want to test whether relatability and knowledge gains can be improved by using a physical robot compared to using a simulator confined to a local device. 

\bigskip\noindent
What we are doing is the first thesis in this area for the \chirp team. We are breaking new ground for the team, establishing collaborations and hopefully providing the basis for future work. 
Because of this we've designed our system implementation in such a way that others can expand upon it. 
%What we have implemented is designed in a way for other students to expand on. We are taking the first step. It is always the hardest. 
%There is also help in the literature but limited in this area. 

\bigskip\noindent
All we have done leads up to a pilot test at the Trondheim International School (THIS), where we tested our hypothesis and how well suited the \chirp robot was in an educational setting. 

\bigskip\noindent
The contact established between the \chirp team and the school will hopefully help foster further research within educational robotics from the \chirp team.
%We successfully created contact with them and will hopefully create a cooperation with the ChIRP group for future research. 

\input{introduction/context}
\input{introduction/motivation}
\input{introduction/goals}
\input{introduction/structure}
